\documentclass[margin,line,pifont,palatino,courier]{res}
\usepackage[hidelinks]{hyperref} % on toshiba
%\usepackage{pifont}
\usepackage[latin1] { inputenc}
\usepackage{wasysym}
\usepackage{marvosym}
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}
%\topmargin .5in
%\oddsidemargin -.5in
%\evensidemargin -.5in
%\textwidth=6.0in
 \textheight=9.0in
%\itemsep=0in
%\parsep=0in
\usepackage{fancyhdr}
%\topmargin=0in
%\textheight=8.5in
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
%\cfoot{\thepage}
%\lfoot{\textit{\footnotesize Research Statement}}
\rfoot{{\footnotesize Curriculum Vitae, Abhishek Pandey, \thepage}}


\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{\Huge \bf \sc Abhishek Pandey \vspace*{.1in}}


\begin{resume}


\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{2.7in}p{2in}}
Yale School of Public Health       & \Telefon ~+1 203  732-7682 \\
135 College Street, Office No: 218       & \Letter~ \verb+abhishek.pandey@yale.edu+\\
New Haven, CT 06510, USA             & %\Mundus~  ~\verb+http://abhiganit.github.io/+
\end{tabular}


\section{\sc Research Interests}
\begin{itemize}
\item Mathematical epidemiology and evolution of infectious
diseases.
\item Evaluating effectiveness and cost-effectiveness of public
health interventions.
\item Computational dynamical systems and Optimization.
\end{itemize}
\section{\sc Employment History}
{\bf  Associate Research Scientist, Oct 2016-current}\\
 \vspace*{-.1in}
\begin{list1}
\item[] Yale School of Public Health, Center for Infectious Disease
  Modeling and Analysis
\end{list1}

{\bf  Postdoctoral Associate, July 2014-Sept 2016}\\
 \vspace*{-.1in}
\begin{list1}
\item[] Yale School of Public Health, Center for Infectious Disease
  Modeling and Analysis
\begin{list2}
\vspace*{.05in}
\item Mentor: Prof.~Alison Galvani
\end{list2}
\end{list1}

\section{\sc Honors}
\textbf{Brown Coxe Postdoctoral Fellowship, July 2015-June 2016 }

\section{\sc Education}

{\bf Ph.D.~in Mathematics, May 2014}\\
\vspace*{-.1in}
\begin{list1}
\item[] Clemson University, Department of Mathematical Sciences

\begin{list2}
\vspace*{.05in}
\item Thesis:  Modeling dengue transmission and vaccination
\item Advisors: Dr.~Jan Medlock and Dr.~Anuj Mubayi
\end{list2}
\end{list1}

{\bf M.S.~in Mathematics, May 2011}\\
\vspace*{-.1in}
\begin{list1}
\item[] Clemson University, Department of Mathematical Sciences
\begin{list2}
\vspace*{.05in}
\item Project:  Modeling and optimization of the allocation of a new dengue vaccine
\item Advisor: Dr.~Jan Medlock
\item GPA: 4.0/4.0
\end{list2}
\end{list1}

{\bf  M.Sc.~in Applied Mathematics, May 2008} \\
\vspace*{-.1in}
\begin{list1}
\item[] Indian Institute of Technology Roorkee, Department of Mathematics

\begin{list2}
\vspace*{.05in}
\item Dissertation:  Stability of LFSR based shift registers
\item Advisor: Dr.~Sugat Gangopadhyay
\item GPA: 7.24/10
\end{list2}

\end{list1}

{\bf B.Sc.~in  Mathematics, May 2006}\\
\vspace*{-.1in}
\begin{list1}
\item[] Delhi University, Ramjas College
\end{list1}



\section{\sc Publications}
\textbf{A.~Pandey*}, C.~Wells*, A.S.~Parpia, M.C.~Fitzpatrick,
B.H.~Singer, A.~Galvani. {Ebola vaccination in Democratic Republic of
  Congo}: In press at~\textit{Proceedings of
  National Academy of Sciences}.

\textbf{A.~Pandey}, M.C.~Fitzpatrick, A.P~Galvani. {Metrics and
  benchmarks for HIV transition-Author's
  reply}. \doilink{10.1016/S2352-3018(19)30049-9}~\textit{Lancet
HIV}.

G.~Akudibillah, \textbf{A.~Pandey}, J.~Medlock. {Optimal control for
  HIV treatment}. \\ \doilink{10.3934/mbe.2019018}~\textit{Mathematical Biosciences and Engineering}.

A.~Galvani, \textbf{A.~Pandey}, M.C.~Fitzpatrick, J.~Medlock,
G.~Gray. {Defining control of the HIV pandemic}.
\doilink{10.1016/S2352-3018(18)30178-4}~\textit{Lancet HIV}.

K.S.~Rock, M.L.~Ndeffo-Mbah, S.~Castano, C.~Palmer,
\textbf{A.~Pandey}, K.E.~Atkins, J.M.~Ndung'u, T.D.~Hollingsworth,
A.~Galvani, C.~Bever, N.~Chitnis, M.J.~Keeling. {Assessing strategies
  against gambiense sleeping sickness through mathematical
  modeling}. \doilink{10.1093/cid/ciy018}~\textit{Clinical Infectious Diseases}.

P.~Sah, M.C.~Fitzpatrick, \textbf{A.~Pandey}, A.~Galvani. {HIV
  criminalization exacerbates subpar diagnosis and treatment across
  the United States: response to the `Association of HIV diagnosis
  rates and laws criminalizing HIV exposure in the United States'}.
\doilink{10.1097/QAD.0000000000001636}~\textit{AIDS}.

J.~Medlock, \textbf{A.~Pandey}, A.S.~Parpia, A.~Tang, L.A.~Skrip,
A.P.~Galvani. {Effectiveness of UNAIDS targets and HIV vaccination
  across 127
  countries}. \doilink{10.1073/pnas.1620788114}~\textit{Proceedings of
  National Academy of Sciences}.

G.~Akudibillah, \textbf{A.~Pandey}, J.~Medlock. {Maximizing the benefits of ART and PrEP in resource-limited settings
}. \doilink{10.1017/S0950268816002958}~\textit{Epidemiology and Infection}.


\textbf{A.~Pandey*}, K.S.~Rock*, M.L.~Ndeffo-Mbah, K.E.~Atkins,
C.~Lumbala, A.~Galvani, M.J.~Keeling. {Data-driven
models to predict the elimination of sleeping sickness in former
Equateur province of DRC}. \doilink{10.1016/j.epidem.2017.01.006}~\textit{Epidemics}.

\textbf{A.~Pandey} and A.~Galvani. {Strategies for \textit{Trypanosoma
  brucei gambiense} elimination}. \doilink{10.1016/S2214-109X(16)30284-4
}~\textit{The Lancet Global Health}.

M.C.~Fitzpatrick, H.A.~Shah, \textbf{A.~Pandey}, A.M.~Bilinski,
M.~Kakkar, A.D.~Clark, J.P.~Townsend, S.S.~Abbas, A.P.~Galvani. {One
  Health approach to cost-effective rabies control in
  India}. \doilink{10.1073/pnas.1604975113}~\textit{Proceedings of National Academy of
  Sciences}.

\textbf{A. ~Pandey*}, K.~Atkins*, N.~Wenzel, L.~Skirp, D.~Yamin,
M.~Ndeffo-Mbah, T.~Nyenswah, M.~Fallah, L.~Bawo, J.~Medlock,
F.~Altice,J.~Townsend,  and A.~Galvani. {Retrospective analysis of
2014-5 Ebola Epidemic in Liberia}. \doilink{10.4269/ajtmh.15-0328}
~\textit{American Journal of Tropical Medicine and Hygiene}.

T.D.~Hollingsworth, E.R.Adams, [et al. including
\textbf{A.~Pandey}]. {Qualitative analyses of modelling to support
  achievement of the 2020 goals for nice neglected tropical
  diseases}. \doilink{10.1186/s13071-015-1235-1} ~\textit{Parasites \& Vectors}.

\textbf{A. ~Pandey}, K.~Atkins, B.~Bucheton, M.~Camara, S.~Aksoy, A.~Galvani
and M.~Ndeffo-Mbah. {Evaluating long-term effectiveness of sleeping
  sickness control measures in Guinea}. \doilink{10.1186/s13071-015-1121-x} ~\textit{Parasites \& Vectors}.

\textbf{A.~Pandey}, and J.~Medlock. {The introduction of denuge vaccine
may temporarily cause large spikes in
prevalence}. \doilink{10.1017/S0950268814001939} ~\textit{Epidemiology and Infection}.

\textbf{A. ~Pandey*}, K.~Atkins*, J.~Medlock, N.~Wenzel,M.~Ndeffo-Mbah,
J.~Townsend, J.~Childs, T.~Nyenswah, and A.~Galvani. {Strategies
  for Containing Ebola in West Africa}. \doilink{10.1126/science.1260612} ~\textit{Science}.

\textbf{A.~Pandey}, A.~Mubayi and J.~Medlock.  {Comparing
  vector--host and SIR models for dengue
  transmission}. \doilink{10.1016/j.mbs.2013.10.007}
~\textit{Mathematical BioSciences}.



% \textbf{A. ~Pandey}, J.~Medlock and A.~Mubayi. {The role of
%   population immunity for accurately estimating model parameters for
%   dengue transmission}. Preprint.

% G.~Akudibillah, J.~Medlock, \textbf{A.~Pandey}, T.~Reluga, C.~Wilson. {Demographically driven backward bifurcations}.
% Book Chapter, Preprint.


%A. Smith and J. Doe,  \textit{Semiclassical generalization
%of the Darboux-Christoffel formula,} J. Math. Phys. \textbf{43}
%(1996), no. 10, 4668-4680.


\section{\sc Selected \\ Talks}

\emph{Comparing models of dengue transmission in Thailand and
  variability in the estimates of $R_0$ among studies}, SIAM Annual
Meeting, Chicago, July 2014


\emph{The introduction of dengue vaccine may temporarily cause large spikes in prevalence}, Spring Central AMS Sectional Meeting,
Texas Tech University, April 2014.

% \emph{Transient Spikes after Vaccination Introduction}, $38^{th}$ Annual SIAM Southeastern Atlantic Section Conference,
% Florida Institute of Technology, March 2014.

% \emph{The introduction of dengue vaccine may cause temporary spikes in prevalence},
% The Third SIAM Gators Student Conference, University of Florida, March 2014.

% \emph{Transient Spikes after Vaccination Introduction}, Math Club, Department of Mathematical Sciences, Clemson University, October 2013.

\emph{Transient Spikes after Vaccination Introduction}, The Fourth International Conference on Mathematical
Modeling and Analysis, Texas Tech University, October 2013.

\emph{Comparing vector--host and SIR models for dengue transmission}, The Society for Mathematical Biology
Annual Meeting and Conference, Arizona State University, June 2013.

\emph{Mathematical Modeling of Dengue Transmission}, Mathematical Biology Seminar, Oregon State University, November 2012.


% \emph{Modeling and Optimization of the Allocation of a New Dengue Vaccine},
% Graduate Student Seminar, Clemson University, May 2011.

% \emph{Estimating Parameters of Dengue Models}, Biomedical Research Retreat, Oregon State University, August 2012.

% \emph{Parameter Estimation and Model Selection for Dengue Transmission}, $1073^ {rd} $ AMS
% Sectional Meeting, Wake Forest University, September 2011.


%\emph{A simple piston problem}, Workshop on Dynamical Systems and
%Related Topics, University of Maryland, College Park. (March 1996)

%\newpage

\section{\sc Posters}

\emph{Comparing vector--host and SIR models for dengue transmission},
The Society for Mathematical Biology Annual Meeting and Conference,
Tempe, Arizona, June 2013.

\emph{Bayesian MCMC Estimation for a Dengue Model}, SIAM Annual
Meeting, Minneapolis, Minnesota, July 2012.

\emph{Parameter Estimation and Model Selection for Dengue
  Transmission}, DIMACS/MBI Workshop on Genetics and Disease Control,
Cape Coast, Ghana, August 2011.

\emph{Parameter Estimation and Model Selection for Dengue
  Transmission}, CBMS Mathematical Epidemiology with Applications,
East Tennessee State University, July 2011.


\section{\sc Work \\ Experience}
Research Assistant, Spring 2014 \\
Department of Mathematical Sciences, Clemson University \\
School of Public Health, Yale University \\
Mentor: Prof.~Alison Galvani

Research Assistant, Summer 2012--Summer 2013 \\
Department of Biomedical Sciences, Oregon State University \\
Mentor: Dr.~Jan Medlock


Research Assistant, Fall 2009--Spring 2010 \\
Department of Mathematical Sciences, Clemson University \\
Mentor: Dr.~Jan Medlock

Instructor, Spring 2012, Fall 2011, Fall 2010, Fall 2013 \\
Department of Mathematical Sciences, Clemson University

Teaching Assistant, Fall 2008--Summer 2009, Summer 2010, \\
Spring 2011--Summer 2011 \\
Department of Mathematical Sciences, Clemson University

\newpage
\section{\sc Teaching \\ Experience}

Calculus of Several Variables (Undergraduate), Fall 2013  \\
Department of Mathematical Sciences, Clemson University

Experimental Statistics Lab (Undergraduate), Spring 2012, Fall 2011 \\
Department of Mathematical Sciences, Clemson University

Calculus of a Single Variable (Undergraduate), Fall 2010 \\
Department of Mathematical Sciences, Clemson University

%\newpage

%\begin{tabular}{@{}p{0.8in}p{4in}}
%1988--1992 & Chancellor's Scholar, University of California at Berkeley \\
%1988--1992 & National Merit Scholar\\
%\end{tabular}


%\newpage


% \section{\sc Graduate Coursework}

% \begin{tabular}{@{}p{2.3in}p{3in}}
% \begin{list1}
% \item Probability
% \item Data Analysis
% \item Statistical Inference
% \item Mathematical Programming
% \item Advanced Linear Programming
% \item Network Flow Programming
% \item Scientific Computing
% \item Advanced Numerical Analysis
% \item Dynamical Neural Networks

% \end{list1}
% &
% \begin{list1}
% \item Dynamical Systems Theory
% \item Difference Equations
% \item Discrete Mathematical Biology
% \item Matrix Analysis
% \item Abstract Algebra
% \item Linear Analysis
% \item Measure Theory and Integration
% \item Applied Mathematics
% \item Calculus of Variations and Optimal Control

% \end{list1}

% \end{tabular}


\section{\sc Academic \\ Activities}
Organizer, Minisymposia: \textit{Applications of Data-driven Models
  from Scientific Research to Public Health Issues} \\
SIAM Annual Meeting, Chicago, Illinois, July 2014

Organizer, Minisymposia: \textit{Modeling Infectious Diseases and Control Strategies} \\
$38^{th}$ Annual SIAM Southeastern Atlantic Section Conference, Florida Institute of Technology, March 2014

Member, Society of Industrial and Applied Mathematics (SIAM)
and American Mathematical Society (AMS)

Class Representative, Session 2007--2008, Session 2006--2007  \\
Department of Mathematics, Indian Institute of Technology Roorkee

Treasurer, Cognizance 2008 (Annual Technical Festival) \\
Department of Mathematics, Indian Institute of Technology Roorkee

\section{\sc Computer \\ Skills}

\begin{tabular}{@{}p{1.2in}p{6in}}

Operating Systems:& Windows 7/8/10, Linux\\
Languages: & C/C++, Python, MATLAB, R \\
Applications: & \LaTeX, Lyx, Office, Sage, Mathematica, Berkeley-Madonna, Lindo
\end{tabular}

%\newpage

% \section{\sc Memberships}

% Society for Industrial and Applied Mathematics (SIAM)

% \vspace*{-.13in}
% American Mathematical Society (AMS)

% \vspace*{-.13in}
% The Society of Mathematical Biology (SMB)

% \vspace*{-.13in}
% Phi Kappa Phi Honor Society

%\newpage

\section{\sc References}
{\bf Alison Galvani}, Burnett and Stender Families Professor, Epidemiology (Microbial),Yale School of Public Health, Yale University
\texttt{alison.galvani@yale.edu}

{\bf Jan Medlock}, Associate Professor, Department of Biomedical Sciences,
Oregon State University,
\texttt{jan.medlock@oregonstate.edu}

{\bf Anuj Mubayi}, Assistant Professor, School of Mathematical and
Natural Sciences, Arizona State University,
\texttt{amubayi@asu.edu}



% {\bf Elena S. Dimitrova}, Associate Professor, Department of Mathematical
% Sciences, Clemson University, SC 29634-0975, (864) 656-1524,
% \texttt{edimit@clemson.edu}



\section{\sc Last \\ Updated}  \today

\end{resume}
\end{document}
